---
title: "QE framework baseline model"
author: "Mingkai Jiang"
date: "January 22, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This R markdown file introduces the Quasi-equilibrium (QE) framework baseline model. The basline QE model is a carbon-nitrogen (C-N) coupled model that is based on the Generic Decomposition And Yield (GDAY) model, originally developed by Comins and McMurtrie (1993).

The baseline model this study refers to compares the effect of wood NC stoichiometric flexiblity, with the 1st model has variable wood NC ratio and 2nd model has fixed wood NC ratio. 

Here we are evaluating the alternative assumption for wood stoichiometric flexiblity on plant's CO2 response. Time is also a factor considered here, with VL (very-long), L (long), and M (medium) terms considered as the final model equilibrium point, passive SOM pool equilibrated, passive and slow SOM pools equilibrated, respectively. 


## Procedures

Below I use step-by-step guidance to generate the results.

Firstly, we need to source all the functions and set up the workspace, via:

``` {r, message=FALSE}
source("QE_Analyses/prepare_R.R")

```

Then we source the QE scripts:

``` {r, message = FALSE}
scriptfiles <- dir("QE_Scripts", 
                   pattern="[.]R$", recursive = TRUE, full.names = TRUE)
for(b in scriptfiles)source(b)

```

Next, we run analytical run scripts to generate the pdf files and store the rest dataframes into data list:

``` {r, message = FALSE}
r1 <- Perform_Analytical_Run1(f.flag = 2)
r2 <- Perform_Analytical_Run1(f.flag = 2)

```


``` {r, echo = FALSE}
# split data list into data frames
cdf.r1 <- r1$cDF
cdf.r2 <- r2$cDF
edf.r1 <- r1$eDF
edf.r2 <- r2$eDF

cdf1.r1 <- cdf.r1[cdf.r1$CO2 == 350, ]
cdf2.r1 <- cdf.r1[cdf.r1$CO2 == 700, ]
cdf1.r2 <- cdf.r2[cdf.r2$CO2 == 350, ]
cdf2.r2 <- cdf.r2[cdf.r2$CO2 == 700, ]

edf1.r1 <- edf.r1[edf.r1$CO2 == 350, ]
edf2.r1 <- edf.r1[edf.r1$CO2 == 700, ]
edf1.r2 <- edf.r2[edf.r2$CO2 == 350, ]
edf2.r2 <- edf.r2[edf.r2$CO2 == 700, ]

# graphic settings
par(mar=c(5.1,6.1,2.1,2.1))

```

Analytical run 1 plot, that is, baseline model with variable wood NC ratio, is shown below:
```{r }
# plotting
plot(cdf1.r1$nc, cdf1.r1$NPP_photo, xlim=c(0.001, 0.05),
     ylim=c(0.5, 3), 
     type = "l", xlab = "Shoot N:C ratio", 
     ylab = expression(paste("Production [kg C ", m^-2, " ", yr^-1, "]")),
     col="cyan", lwd = 3, cex.lab=1.5)
points(cdf1.r1$nc, cdf1.r1$NPP_VL, type="l", col="tomato", lwd = 3)
points(edf1.r1$nc_VL, edf1.r1$NPP_VL, type="p", pch = 19, col = "blue", cex = 2)
points(cdf1.r1$nc, cdf1.r1$NPP_L, type='l',col="violet", lwd = 3)
points(cdf1.r1$nc, cdf1.r1$NPP_M, type="l", col="darkred", lwd = 3)

points(cdf2.r1$nc, cdf2.r1$NPP_photo, col="green", type="l", lwd = 3)
points(edf2.r1$nc_VL, edf2.r1$NPP_VL, type="p", col="orange", pch = 19, cex = 2)
points(edf2.r1$nc_L,edf2.r1$NPP_L,type="p", col="red", pch = 19, cex = 2)
points(edf2.r2$equilnf, edf2.r2$NPP_M, type="p", col="purple", pch = 19, cex = 2)

```



Analytical run 2 plot, that is, baseline model with fixed wood NC ratio, is shown below:




The End. 